Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-01-31 paperMSR.tex
Parrafo de la contribucion del articulo

With this paper we try to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug. Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software. Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process. \grex{reescribir este parrafo para que quede mas claro.}

@@

\gema{Puedes elaborar un poco mas el parrafo anterior? Puede ser en castellano}

@@

In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs. \grex{Tengo que elaborar mas esto, que es el punto fuerte del articulo.}

>>>>

The main contribution of this paper is to shed some light on the correctness of the asumption that a bug is caused in the previous commit. In the point of time where the previous commit was performed, the lines that are modified in the bug-fix were correct. We show that a significant portion of bugs can be attributed to other causes, offering evidence that all the research findings and methods that have been constructed based on this assumption are not using accurate data and may give inaccurate results. Finally, our study can be understood as a step forward to better understand the bug seeding process.

@@

\grex{Puedes elaborar un poco mas el parrafo (y los puntos) anterior(es)? Puede ser en castellano.}

@@

In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs. \grex{Tengo que elaborar mas esto, que es el punto mas fuerte (o de mayor) del articulo.}
